Reasoning Graphically about Quantum Computation

### 2008-02-28 papers/reasoning-graphically/paper.tex
working on reaosning section
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1383 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

Like the notation for variable-node graphs, we use $G \leq H$ to
denote that $G$ matches $H$.

@@

\begin{theorem}
  \emph{!-Matching respects !-box semantics}: $G \leq H
  \Leftrightarrow \binterp{G} \supseteq \binterp{H}$. The proof is a
  simple consequence from the defintion of $\binterp{G}$ being a
  subset of the graphs that match $G$.
\end{theorem}

@@

@@

The formalism we have presented for graph patterns provides a
\emph{meta-level} framework for reasoning in some model of concrete
graphs. The chosen model provides the \emph{object-level} graph
formalism. This includes a particular representation for data at the
nodes and edges as well as node-matching and edge-matching
algorithms. The object-level definition also defines a set of
axiomatic equational rules. These are derived

\subsubsection{Soundness.} An object-level graph system is sound if
their is some equation which can not be derived.

 The soundness
of a set of axioms in our framework

 framework
requres the model is an instance of a compact closed category, and
that the

For the model we use of qantum computation, this is finite
dimensional hilbert spaces. Because the basic equational rules come
from a model and have been proved for that model, the resulting
preserve the soundness of our graphical system.

 and the families of them represneted by graph
patterns.

An object graph formalsism uses the

@@

@@

\subsection{Unification}
\subsection{Substitution}

\subsection{Node in Quantum Computations}
\label{ssec:node-expressions}

 Expressions

>>>>

\noindent We use $G \leq_! H$ to denote that $G$ matches $H$.

@@

\begin{theorem}
  \emph{!-Matching respects !-box semantics}: $G \leq_! H
  \Leftrightarrow \binterp{G} \supseteq \binterp{H}$. The proof is a
  simple consequence from the defintion of $\binterp{G}$ being a
  subset of the graphs that match $G$.
\end{theorem}

@@

Rules that have been proved for concrete graphs, such as the
Frombenius Law, are in fact a family of proofs that correspond to
replacing the boundary edges with variable nodes. This is beacuse of
the symmetry of rules in a compact closed categories:

@@

The formalism we have presented for graph patterns provides a
\emph{meta-level} framework for reasoning in some model of concrete
graphs.

An \emph{object-level} graph formalism is defined by some
model of a compact closed category.

This includes a particular
representation for data at the nodes and edges as well as
node-matching and edge-matching algorithms. The object-level
definition also defines a set of axiomatic equational rules.

@@

\subsubsection{Soundness.} An object-level graph system is sound if
their is some pair of graphs which can not be derived as an equation.

To ensure soundness, it is sufficient to show that the object-level
model is a compact-closed category and that the basic equational rules
of the object-level can be proved in the underlying model.

\subsubsection{Completeness.} A formalism for graphs can be shown to
be complete with respect to the underlying semantics if the equational
rules have been shown to be complete.

@@

\section{A Case Study in Quantum Computation}

The model we are interested in is finite dimensional hilbert spaces as
an account of qantum computation.

\subsection{Node Expressions}
\label{ssec:node-expressions}

Completeness is a challenging and still open problem for graph based
models of quantum computation. However, even without completeness
interesting quantum computations can be expressed.
